% general APT observations
UZE & temperature & ifno or boundname & -- & uze cell temperature. If boundname is specified, boundname must be unique for each uze cell. \\
UZE & flow-ja-face & ifno or boundname & ifno or -- & Energy flow between two uze cells.  If a boundname is specified for ID1, then the result is the total energy flow for all uze cells. If a boundname is specified for ID1 then ID2 is not used.\\
UZE & storage & ifno or boundname & -- & Simulated energy storage flow rate for a uze cell or group of uze cells. \\
UZE & constant & ifno or boundname & -- & Simulated energy constant-flow rate for a uze cell or a group of uze cells. \\
UZE & from-mvr & ifno or boundname & -- & Simulated energy inflow into a uze cell or group of uze cells from the MVE package. Energy inflow is calculated as the product of provider temperature and the mover flow rate. \\
UZE & uze & ifno or boundname & -- & Energy flow rate for a uze cell or group of uze cells and its aquifer connection(s). \\

%observations specific to the uze package
% infiltration rej-inf uzet rej-inf-to-mvr
UZE & infiltration & ifno or boundname & -- & Infiltration rate applied to a uze cell or group of uze cells multiplied by the infiltration temperature. \\
UZE & rej-inf & ifno or boundname & -- & Rejected infiltration rate applied to a uze cell or group of uze cells multiplied by the infiltration temperature. \\
UZE & uzet & ifno or boundname & -- & Unsaturated zone evapotranspiration rate applied to a uze cell or group of uze cells multiplied by the latent heat of vaporization, heat capacity of the simulated fluid, and density of the simulated flued. \\
UZE & rej-inf-to-mvr & ifno or boundname & -- & Rejected infiltration rate applied to a uze cell or group of uze cells multiplied by the infiltration temperature that is sent to the mover package. \\
