% general APT observations
LKE & temperature & ifno or boundname & -- & Lake temperature. If boundname is specified, boundname must be unique for each lake. \\
LKE & flow-ja-face & ifno or boundname & ifno or -- & Energy flow between two lakes connected by an outlet.  If more than one outlet is used to connect the same two lakes, then the energy flow for only the first outlet can be observed.  If a boundname is specified for ID1, then the result is the total energy flow for all outlets for a lake. If a boundname is specified for ID1 then ID2 is not used.\\
LKE & storage & ifno or boundname & -- & Simulated energy storage flow rate for a lake or group of lakes. \\
LKE & constant & ifno or boundname & -- & Simulated energy constant-flow rate for a lake or group of lakes. \\
LKE & from-mvr & ifno or boundname & -- & Simulated energy inflow into a lake or group of lakes from the MVE package. Energy inflow is calculated as the product of provider temperature and the mover flow rate. \\
LKE & to-mvr & outletno or boundname & -- & Energy outflow from a lake outlet, a lake, or a group of lakes that is available for the MVR package. If boundname is not specified for ID, then the outflow available for the MVR package from a specific lake outlet is observed. In this case, ID is the outlet number, which must be between 1 and NOUTLETS. \\
LKE & lkt & ifno or boundname & \texttt{iconn} or -- & Energy flow rate for a lake or group of lakes and its aquifer connection(s). If boundname is not specified for ID, then the simulated lake-aquifer flow rate at a specific lake connection is observed. In this case, ID2 must be specified and is the connection number \texttt{iconn} for lake \texttt{ifno}. \\

%observations specific to the lake package
% rainfall evaporation runoff ext-inflow withdrawal outflow
LKE & rainfall & ifno or boundname & -- & Rainfall rate applied to a lake or group of lakes multiplied by the rainfall temperature. \\
LKE & evaporation & ifno or boundname & -- & Simulated evaporation rate from a lake or group of lakes multiplied by latent heat of vaporization, heat capcity of the simulated fluid, and the density of the simulated fluid. \\
LKE & runoff & ifno or boundname & -- & Runoff rate applied to a lake or group of lakes multiplied by the runoff temperature. \\
LKE & ext-inflow & ifno or boundname & -- & Energy inflow into a lake or group of lakes calculated as the external inflow rate multiplied by the inflow temperature. \\
LKE & withdrawal & ifno or boundname & -- & Specified withdrawal rate from a lake or group of lakes multiplied by the simulated lake temperature. \\
LKE & ext-outflow & ifno or boundname & -- & External outflow from a lake or a group of lakes, through their outlets, to an external boundary.  If the water mover is active, the reported ext-outflow value plus the rate to mover is equal to the total outlet outflow.

%LKE & outlet-inflow & ifno or boundname & -- & Simulated inflow from upstream lake outlets into a lake or group of lakes. \\
%LKE & inflow & ifno or boundname & -- & Sum of specified inflow and simulated inflow from upstream lake outlets into a lake or group of lakes. \\
%LKE & outlet & outletno or boundname & -- & Simulate outlet flow rate from a lake outlet, a lake, or a group of lakes. If boundname is not specified for ID, then the flow from a specific lake outlet is observed. In this case, ID is the outlet number outletno. \\
%LKE & volume & ifno or boundname & -- & Simulated lake volume or group of lakes. \\
%LKE & surface-area & ifno or boundname & -- & Simulated surface area for a lake or group of lakes. \\
%LKE & wetted-area & ifno or boundname & \texttt{iconn} or -- & Simulated wetted-area for a lake or group of lakes and its aquifer connection(s). If boundname is not specified for ID, then the wetted area of a specific lake connection is observed. In this case, ID2 must be specified and is the connection number \texttt{iconn}. \\
%LKE & conductance & ifno or boundname & \texttt{iconn} or -- & Calculated conductance for a lake or group of lakes and its aquifer connection(s). If boundname is not specified for ID, then the calculated conductance of a specific lake connection is observed. In this case, ID2 must be specified and is the connection number \texttt{iconn}.
