SFR & stage & ifno or boundname & -- & Surface-water stage in a stream-reach boundary. If boundname is specified, boundname must be unique for each reach. \\
SFR & ext-inflow & ifno or boundname & -- & Inflow into a stream-reach from an external boundary for a stream-reach or a group of stream-reaches. \\
SFR & inflow & ifno or boundname & -- & Inflow into a stream-reach from upstream reaches for a stream-reach or a group of stream-reaches. \\
SFR & from-mvr & ifno or boundname & -- & Inflow into a stream-reach from the MVR package for a stream-reach or a group of stream-reaches. \\
SFR & rainfall & ifno or boundname & -- & Rainfall rate applied to a stream-reach or a group of stream-reaches. \\
SFR & runoff & ifno or boundname & -- & Runoff rate applied to a stream-reach or a group of stream-reaches. \\
SFR & sfr & ifno or boundname & -- & Simulated flow rate for a stream-reach and its aquifer connection for a stream-reach or a group of stream-reaches. \\
SFR & evaporation & ifno or boundname & -- & Simulated evaporation rate from a stream-reach or a group of stream-reaches. \\
SFR & outflow & ifno or boundname & -- & Outflow from a stream-reach to downstream reaches for a stream-reach or a group of stream-reaches. \\
SFR & ext-outflow & ifno or boundname & -- & Outflow from a stream-reach to an external boundary for a stream-reach or a group of stream-reaches. \\
SFR & to-mvr & ifno or boundname & -- & Outflow from a stream-reach that is available for the MVR package for a stream-reach or a group of stream-reaches. \\
SFR & upstream-flow & ifno or boundname & -- & Upstream flow for a stream-reach or a group of stream-reaches from upstream reaches and the MVR package. \\
SFR & downstream-flow & ifno or boundname & -- & Downstream flow for a stream-reach or a group of stream-reaches prior to diversions and the MVR package. \\
SFR & depth & ifno or boundname & -- & Surface-water depth in a stream-reach boundary. If boundname is specified, boundname must be unique for each reach. \\
SFR & wet-perimeter & ifno or boundname & -- & Wetted perimeter in a stream-reach boundary. If boundname is specified, boundname must be unique for each reach. \\
SFR & wet-area & ifno or boundname & -- & Wetted cross-section area in a stream-reach boundary. If boundname is specified, boundname must be unique for each reach. \\
SFR & wet-width & ifno or boundname & -- & Wetted top width in a stream-reach boundary. If boundname is specified, boundname must be unique for each reach. \\

