MAW & head & wellno or boundname & -- & Head in a multi-aquifer well. If boundname is specified, boundname must be unique for each multi-aquifer well. \\
MAW & from-mvr & wellno or boundname & -- & Simulated inflow to a well from the MVR package for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & maw & wellno or boundname & \texttt{icon} or -- & Simulated flow rate for a multi-aquifer well or a group of multi-aquifer wells and its aquifer connection(s). If boundname is not specified for ID, then the simulated multi-aquifer well-aquifer flow rate at a specific multi-aquifer well connection is observed. In this case, ID2 must be specified and is the connection number \texttt{icon}. \\
MAW & rate & wellno or boundname & -- & Simulated pumping rate for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & rate-to-mvr & wellno or boundname & -- & Simulated well discharge that is available for the MVR package for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & fw-rate & wellno or boundname & -- & Simulated flowing well flow rate for a multi-aquifer well or a group of multi-aquifer wells.  \\
MAW & fw-to-mvr & wellno or boundname & -- & Simulated flowing well discharge rate that is available for the MVR package for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & storage & wellno or boundname & -- & Simulated storage flow rate for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & constant & wellno or boundname & -- & Simulated constant-flow rate for a multi-aquifer well or a group of multi-aquifer wells. \\
MAW & conductance & wellno or boundname & \texttt{icon} or -- & Simulated well conductance for a multi-aquifer well or a group of multi-aquifer wells and its aquifer connection(s). If boundname is not specified for ID, then the simulated multi-aquifer well conductance at a specific multi-aquifer well connection is observed. In this case, ID2 must be specified and is the connection number \texttt{icon}. \\
MAW & fw-conductance & wellno or boundname & -- & Simulated flowing well conductance for a multi-aquifer well or a group of multi-aquifer wells.