UZF & uzf-gwrch & uzfno or boundname & -- & Simulated recharge to the aquifer calculated by the UZF package for a UZF cell or a group of UZF cells.\\
UZF & uzf-gwd & uzfno or boundname & -- & Simulated groundwater discharge to the land surface calculated by the UZF package for a UZF cell or a group of UZF cells. \\
UZF & uzf-gwd-to-mvr & uzfno or boundname & -- & Simulated groundwater discharge to the land surface calculated by the UZF package that is available to the MVR package for a UZF cell or a group of UZF cells. \\
UZF & uzf-gwet & uzfno or boundname & -- & Simulated groundwater evapotranspiration calculated by the UZF package for a UZF cell or a group of UZF cells.\\
UZF & infiltration & uzfno or boundname & -- & Specified infiltration rate applied to a UZF package for a UZF cell or a group of UZF cells with landflag values not equal to zero.\\
UZF & from-mvr & uzfno or boundname & -- & Inflow into a UZF cell from the MVR package for a UZF cell or a group of UZF cells. \\
UZF & rej-inf & uzfno or boundname & -- & Simulated rejected infiltration calculated by the UZF package for a UZF cell or a group of UZF cells. \\
UZF & rej-inf-to-mvr & uzfno or boundname & -- & Simulated rejected infiltration calculated by the UZF package that is available to the MVR package for a UZF cell or a group of UZF cells. \\
UZF & uzet & uzfno or boundname & -- & Simulated unsaturated evapotranspiration calculated by the UZF package for a UZF cell or a group of UZF cells.\\
UZF & storage & uzfno or boundname & -- & Simulated storage flow rate for a UZF package cell or a group of UZF cells. \\
UZF & net-infiltration & uzfno or boundname & -- & Simulated net infiltration rate for a UZF package cell or a group of UZF cells. \\
UZF & water-content & uzfno or boundname & depth & Unsaturated-zone water content at a user-specified depth (ID2) relative to the top of GWF cellid for a UZF cell. The user-specified depth must be greater than or equal to zero and less than the thickness of GWF cellid (TOP - BOT). If boundname is specified, boundname must be unique for each UZF cell.