% general APT observations
MWT & concentration & ifno or boundname & -- & Well concentration. If boundname is specified, boundname must be unique for each well. \\
%flowjaface not included
MWT & storage & ifno or boundname & -- & Simulated mass storage flow rate for a well or group of wells. \\
MWT & constant & ifno or boundname & -- & Simulated mass constant-flow rate for a well or group of wells. \\
MWT & from-mvr & ifno or boundname & -- & Simulated mass inflow into a well or group of wells from the MVT package. Mass inflow is calculated as the product of provider concentration and the mover flow rate. \\
MWT & mwt & ifno or boundname & \texttt{iconn} or -- & Mass flow rate for a well or group of wells and its aquifer connection(s). If boundname is not specified for ID, then the simulated well-aquifer flow rate at a specific well connection is observed. In this case, ID2 must be specified and is the connection number \texttt{iconn} for well \texttt{ifno}. \\

% observations specific to the mwt package
MWT & rate & ifno or boundname & -- & Simulated mass flow rate for a well or group of wells. \\
MWT & fw-rate & ifno or boundname & -- & Simulated mass flow rate for a flowing well or group of flowing wells. \\
MWT & rate-to-mvr & well or boundname & -- & Simulated mass flow rate that is sent to the MVT Package for a well or group of wells.\\
MWT & fw-rate-to-mvr & well or boundname & -- & Simulated mass flow rate that is sent to the MVT Package from a flowing well or group of flowing wells. \\
