% general APT observations
SFT & concentration & ifno or boundname & -- & Reach concentration. If boundname is specified, boundname must be unique for each reach. \\
SFT & flow-ja-face & ifno or boundname & ifno or -- & Mass flow between two reaches.  If a boundname is specified for ID1, then the result is the total mass flow for all reaches. If a boundname is specified for ID1 then ID2 is not used.\\
SFT & storage & ifno or boundname & -- & Simulated mass storage flow rate for a reach or group of reaches. \\
SFT & constant & ifno or boundname & -- & Simulated mass constant-flow rate for a reach or group of reaches. \\
SFT & from-mvr & ifno or boundname & -- & Simulated mass inflow into a reach or group of reaches from the MVT package. Mass inflow is calculated as the product of provider concentration and the mover flow rate. \\
SFT & to-mvr & ifno or boundname & -- & Mass outflow from a reach, or a group of reaches that is available for the MVR package. If boundname is not specified for ID, then the outflow available for the MVR package from a specific reach is observed. \\
SFT & sft & ifno or boundname & -- & Mass flow rate for a reach or group of reaches and its aquifer connection(s). \\

%observations specific to the stream transport package
% rainfall evaporation runoff ext-inflow withdrawal outflow
SFT & rainfall & ifno or boundname & -- & Rainfall rate applied to a reach or group of reaches multiplied by the rainfall concentration. \\
SFT & evaporation & ifno or boundname & -- & Simulated evaporation rate from a reach or group of reaches multiplied by the evaporation concentration. \\
SFT & runoff & ifno or boundname & -- & Runoff rate applied to a reach or group of reaches multiplied by the runoff concentration. \\
SFT & ext-inflow & ifno or boundname & -- & Mass inflow into a reach or group of reaches calculated as the external inflow rate multiplied by the inflow concentration. \\
SFT & ext-outflow & ifno or boundname & -- & External outflow from a reach or group of reaches to an external boundary. If boundname is not specified for ID, then the external outflow from a specific reach is observed. In this case, ID is the reach ifno.
