Particle Release Point (PRP) Package information is read from the file that is specified by ``PRP6'' as the file type.  More than one PRP Package can be specified for a PRT model. 

The PRP Package offers multiple ways to specify particle release times.  Particle release times may either be provided explicitly, relative to the simulation start time, or configured relative to the time discretization of stress periods via period block settings.  When multiple ways of specifying release times are used together, the resulting set of release times is the union of the times specified by each method.

This package contains options to configure how particles behave in dry conditions. Each of these is described in detail below. Their interaction is summarized in the PRT chapter introduction.

\vspace{5mm}
\subsubsection{Structure of Blocks}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/prt-prp-options.dat}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/prt-prp-dimensions.dat}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/prt-prp-packagedata.dat}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/prt-prp-releasetimes.dat}
\vspace{5mm}
\noindent \textit{FOR ANY STRESS PERIOD}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/prt-prp-period.dat}
\packageperioddescription \: If no PERIOD block is specified for any period, a single particle is released from each release point at the beginning of the simulation.
%\noindent All of the stress period information in a PERIOD block will apply only to that stress period; the information will not continue to apply for subsequent stress periods.  Note that this behavior is different from the simple stress packages (CHD, WEL, DRN, RIV,
%GHB, RCH and EVT) and the advanced stress packages (MAW, SFR, LAK, and UZF).

\vspace{5mm}
\subsubsection{Explanation of Variables}
\begin{description}
\input{./mf6ivar/tex/prt-prp-desc.tex}
\end{description}

\vspace{5mm}
\subsubsection{Example Input File}
\lstinputlisting[style=inputfile]{./mf6ivar/examples/prt-prp-example.dat}

