	\subsection{Version mf6.0.0---August 10, 2017}
	
	\textbf{\underline{BUG FIXES AND OTHER CHANGES TO EXISTING FUNCTIONALITY}} \\
	\underline{BASIC FUNCTIONALITY}
	\begin{itemize}
		\item Removed support for the SINGLE observation type.  All observations must be CONTINUOUS, which means observation values are written for every time step. 
		\item Added support for a no-data value (3.0E30), which can be used as a placeholder in a time-series file containing multiple time series. Use of the no-data value facilitates combining separate time series into a single file when the time series contain records for differing simulation times.
		\item Model names specified in the simulation name file cannot have spaces in them.  A check was implemented to terminate with an error if the model name contains spaces.  Model names cannot exceed 16 characters.  Trailing spaces are allowed.
		\item The name and version of the compiler used to make the run file is now written to the terminal and to the simulation list file.
		\item Many of the Fortran source files were modified and reformatted.  Unused variables were removed.
	\end{itemize}
	
	\underline{ADVANCED STRESS PACKAGES}
	\begin{itemize}
		\item Updated MAW package so that well connection conductance calculations correctly account for THICKSTRT in the NPF package for layers that use THICKSTRT (and are confined).
		\item Added \texttt{CUMULATIVE} \texttt{coneqn} (conductance) option to MAW package.
		\item Fixed bug in LAK package weir lake outlet calculation.
		\item Fixed bug in LAK package when internal outlets were specified and combined with the MVR package that was also moving water internally in the same LAK package.
		\item Updated the table created when PRINT\_FLOWS is specified in the LAK package OPTIONS block to include internal flow terms if NOUTLETS is greater than 0. 
		\item Renamed Lake Tables DIMENSIONS block NENTRIES to NROW and added NCOL to DIMENSIONS block.
		\item Eliminated MAXIMUM\_OUTLET\_DEPTH = 10 [L] as default behavior for MANNING and WEIR LAK package lake outlet types. The maximum depth threshold was used in MODFLOW-2005 lake package because a table was used to calculate lake outflows to SFR. Can still use maximum depth threshold in develop versions of MODFLOW~6 by specifying MAXIMUM\_OUTLET\_DEPTH in the options block with a value.
		\item Removed MULTILAYER option for UZF package---this option didn't actually do anything.
		\item Added the requirement that the UZF number be specified as the first value on each line in the PACKAGEDATA block.
		\item Renamed MAXBOUND in the DIMENSIONS block of the SFR Package to be NREACHES.
		\item Implemented a check in the SFR Package to make sure that information is specified in the PACKAGEDATA block for every reach.  Program terminates with an error if information for a reach is not found.
	\end{itemize}
	