The Adaptive Time Step (ATS) utility for the TDIS Package can be activated by specifying the ATS6 option in the TDIS input file.  If activated, \mf will read ATS input according to the following description.

Adaptive time stepping will be used for any stress periods that are listed in the PERIODDATA block of the ATS input file.  If a stress period is adaptive, then the \texttt{nstp} and \texttt{tsmult} parameters in the TDIS input file have no effect on time step progression.  Instead the ATS settings specified for the period are used to control the time step progression.

The ATS implementation implemented in \mf is patterned after the approach implemented in MODFLOW-USG.  There are two fundamental parts to the ATS utility.  The first is the capability to handle failure of a solution to converge.  If ATS is active for a stress period in which the solution fails to converge, then the program will continue to try smaller time steps until convergence is achieved or the length of the time step reaches the lower allowable limit (\texttt{dtmin}).  Once this lower limit on the time step is reached, then the program will follow the established logic for non-adaptive time steps.  That is, the program will either stop and write concluding information, or the program will continue to the next time step if the CONTINUE option is specified in the simulation name file.

The second fundamental part of the ATS utility is dynamic adjustment of the time step size according to simulation behavior.  The ATS utility in \mf has been implemented in a generic and modular manner in which any model, exchange, or solution can submit a preferred time length to be used in determining the time step length.  The ATS utility will proceed with the smallest time step submitted by these different simulation components.  In the present implementation, time steps may be adjusted by the following components.

\begin{itemize}
\item The numerical solution will submit a preferred time step length based on the convergence pattern for the previous time step.  If the numerical solution is relatively easy (as measured by the number of outer iterations), then the length of the next time step will increase by a factor of the \texttt{dtadj} variable.  Conversely, if the solution is difficult to obtain, then the length of the next time step will decrease, by dividing the previous time step length by the \texttt{dtadj} variable.  This time-step adjustment is on by default, but can be turned off by specifying a value of zero for the ATS\_OUTER\_MAXIMUM\_FRACTION option in the Iterative Model Solution (IMS).

\item The Advection (ADV) Package of the Groundwater Transport (GWT) or Groundwater Energy Transport (GWE) Model will submit a maximum time-step length subject to Courant constraints if the user specifies a non-zero value for the ATS\_PERCEL option.
\end{itemize}

In the present ATS implementation, time series variables are interpolated based on the starting and ending times of the time step.  If solution failure was encountered and a time step is retried with a smaller time step size, time series variables are re-interpolated for the shortened time step.  In most cases, this is the intended behavior, however, if time series contain a much finer level of temporal detail, then this additional detail could exacerbate convergence problems.

A limitation with the present ATS implementation is that there is no way to explicitly specify times within a stress period for saving output.  Output can be obtained at the end of a period, and within a period according the Output Control time step settings.  For example, the Output Control settings allow for printing and saving based on the FIRST, LAST, FREQUENCY, and STEPS options, but these are based on time steps, the lengths of which are adaptive and not necessarily known before the simulation.  Thus, there is no way to request output at specific times within a stress period managed by ATS.  If observations are used for models and packages, observations are written for every time step.  For automated parameter estimation applications, additional post-processing of output files may be required in order to align simulated values with measurements.  

\vspace{5mm}
\subsection{Structure of Blocks}
%\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/sim-ats-options.dat}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/utl-ats-dimensions.dat}
\lstinputlisting[style=blockdefinition]{./mf6ivar/tex/utl-ats-perioddata.dat}

\vspace{5mm}
\subsection{Explanation of Variables}
\begin{description}
\input{./mf6ivar/tex/utl-ats-desc.tex}
\end{description}

\vspace{5mm}
\subsection{Example Input File}
\lstinputlisting[style=inputfile]{./mf6ivar/examples/utl-ats-example.dat}

